Magnetic Inhibition of Convection and the Fundamental Properties of Low--Mass Stars

### 2016-02-22 paper/ms.tex
radiative core mass difference figure

@@

{\bf Further work is needed to explore whether magnetic inhibition of convection serves as a robust solution for noted age gradients as a function of stellar spectral type \citep[e.g.,][]{Naylor2009, Herczeg2015}. Previous work determining ages for the $\beta$-Pictoris moving group from magnetic stellar models suggests the solution is robust \citep{MM10, Malo2014, Binks2016}, but additional confirmation using stellar populations with a wider variety of ages is required. These results also highlight the need to explore how the inclusion of magnetic inhibition of convection affects the (sub)stellar initial mass function young stellar populations.}

In the meantime, the use of magnetic stellar models as a component for isochrone analyses for young low-mass stars is recommended. Consistency across the HR and mass-radius diagrams exhibited by magnetic stellar evolution isochrones suggest that magnetic isochrones will provide a more accurate characterization of transiting exoplanet host stars in young stellar populations, especially those observed by \emph{Kepler}/K2 in Upper Scorpius. By adopting an incorrect age, a reasonable estimate of stellar radii can be found, but stellar masses will be systematically underestimated by roughly 30\%. Similar arguments apply to the characterization of young low-mass star hosting directly imaged giant planets or brown dwarfs. Ages inferred from standard model isochrones will be systematically too young by a factor of two resulting in a systematic underestimation of giant planet and brown dwarfs masses by roughly 35\%. To facilitate this work, all models used in this study are available online\footnote{\url{https://github.com/gfeiden/MagneticUpperSco/}}. In addition, a small grid of solar-metallicity magnetic stellar mass tracks and isochrones is under construction, as is a web-interface to compute custom magnetic models.

>>>>

\begin{figure}[t]
    \centering
    \includegraphics[width=0.95\linewidth]{radiative_core_mass_difference.eps}
    \caption{Difference in radiative core mass between magnetic and standard stellar evolution models as a function of effective temperature. The difference is shown as the radiative core mass of a magnetic model minus the radiative core mass of a standard stellar model at the same effective temperature, ($M_{\rm rad.\ core,\, mag} - M_{\rm rad.\ core,\, std}$).}
    \label{fig:delta_mass}
\end{figure}

@@

{\bf Further work is needed to explore whether magnetic inhibition of convection serves as a robust solution for noted age gradients as a function of stellar spectral type \citep[e.g.,][]{Naylor2009, Herczeg2015}. Previous work determining ages for the $\beta$-Pictoris moving group from magnetic stellar models suggests the solution is robust \citep{MM10, Malo2014, Binks2016}, but additional confirmation using stellar populations with a wider variety of ages is required. These results also highlight the need to explore how the inclusion of magnetic inhibition of convection affects the (sub)stellar initial mass function for young stellar populations.}

{\bf In the meantime, the use of magnetic stellar models as a component for isochrone analyses for young low-mass stars is recommended. Consistency across the HR and mass-radius diagrams exhibited by magnetic stellar evolution isochrones suggest that magnetic isochrones will provide a more accurate characterization of transiting exoplanet host stars in young stellar populations, especially those observed by \emph{Kepler}/K2 in Upper Scorpius. By adopting an incorrect age, a reasonable estimate of stellar radii can be found, but stellar masses will be systematically underestimated by roughly 30\%. Similar arguments apply to the characterization of young low-mass stars hosting directly imaged giant planets or brown dwarfs. Ages inferred from standard model isochrones may be systematically too young by a factor of two resulting in a systematic underestimation of giant planet and brown dwarfs masses by roughly 35\% \citep{Baraffe2003}. To facilitate their adoption, all models used in this study are available online\footnote{\url{https://github.com/gfeiden/MagneticUpperSco/}}. A small grid of solar-metallicity magnetic stellar mass tracks and isochrones is also under construction, as is a web-interface to compute custom magnetic models.}
